\textbf{Teaching a machine to generate an artificial universe}

### 2020-10-14 paper.tex
initial draft (fixed abstract)

\twocolumn[
	\begin{@twocolumnfalse}
		\maketitle
		\begin{abstract}
		    This work presents a three-dimensional generative framework that uses an Auxiliary Classifier Generative
		    Adversarial Network to create realistic samples of cosmological structure at various values of redshift~$z$. 
		    Provisional samples of the virtual cosmic web are obtained from N-body simulation data that is restricted to 
		    volumes of size $200 \, h^{-1} \, \text{Mpc}$. The generated samples are shown to demonstrate
		    a high degree of coherence with their simulated counterparts and the distinction is difficult to make visually
		    by human experts. The nature of the separation between generated and N-body simulation samples is quantified 
		    with repeated tests of the Kullback-Leibler divergence on ensembles of samples alongside samples with 
		    uniformly distributed pixel densities. It is found that the implementations secure a coherence to within the
		    same order of magnitude as a self comparison of the simulation samples. The main advantage of the generative
		    approach to simulating large volumes of cosmological structure is that much less time is required than 
		    creating N-body simulations on high performance computing resources. This is demonstrated by the creation of
		    large box volumes made with $\sim10^3$ generated samples for a redshift $z$ arranged on a cubic mesh. At this 
		    stage, the generative artificial intelligence can then be said to be capable of generating an artificial 
		    universe. Future explorations of the method that are relevant to the next paradigm in cosmological simulations 
		    are also outlined. 
		  %  The most pertinent application being for a generator that can produce samples that maintain high statistical 
		  %coherence to simulation data at various redshifts. 
            %\textit{}
		\end{abstract}
	\end{@twocolumnfalse}
]
{\renewcommand{\thefootnote}%
    {\fnsymbol{footnote}}
  \footnotetext[1]{Corresponding author: \url{jedhmr@gmail.com}}
}

>>>>

\twocolumn[
	\begin{@twocolumnfalse}
		\maketitle
		\begin{abstract}
		    This work presents a three-dimensional generative framework that uses an Auxiliary Classifier Generative
		    Adversarial Network to create realistic samples of cosmological structure at various values of redshift~$z$. 
		    Provisional samples of the virtual cosmic web are obtained from N-body simulation data that is restricted to 
		    volumes of size $200 \, h^{-1} \, \text{Mpc}$. The generated samples are shown to demonstrate
		    a high degree of coherence with their simulated counterparts and the distinction is difficult to make visually
		    by human experts. The nature of the separation between generated and N-body simulation samples is quantified 
		    with repeated tests of the Kullback-Leibler divergence on ensembles of samples alongside samples with 
		    uniformly distributed pixel densities. It is found that the implementations secure a coherence to within the
		    same order of magnitude as a self comparison of the simulation samples. Further tests demonstrate this coherence
		    extends to values of redshift $z$ to which the model has never been exposed.
		    The main advantage of the generative
		    approach to simulating large volumes of cosmological structure is that much less time is required than 
		    creating N-body simulations on high performance computing resources. 
		  %  This is demonstrated by the creation of large box volumes made with $\sim10^3$ generated samples for a redshift $z$ arranged on a cubic mesh. 
		    The generator also provides a continuous spectrum of samples across redshift $z$, that is consistent over a 
		    single sample of the cosmic web.
		    At this stage, the generative artificial intelligence can then be said to be capable of creating an artificial 
		    universe. Future explorations of the method that are relevant to the next paradigm in cosmological simulations 
		    are also outlined with reference to modern techniques in the field of artificial intelligence.
		  %  The most pertinent application being for a generator that can produce samples that maintain high statistical 
		  %coherence to simulation data at various redshifts. 
            %\textit{}
		\end{abstract}
	\end{@twocolumnfalse}
]
{\renewcommand{\thefootnote}%
    {\fnsymbol{footnote}}
  \footnotetext[1]{Corresponding author: \url{jedhmr@gmail.com}}
}
